---
title: "p8105_hw5_qw2331"
output: github_document
---

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%",
  message = FALSE
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

**Load the data**
```{r}
homd_df <- read_csv(
  "./data/homicide-data.csv",
  na = c("", "Unknown"))
```

**A brief description**
```{r}
# Using summary or glimpse
summary(homd_df)
```
+ This dataset contains ``r nrow(homd_df)`` observations and ``r ncol(homd_df)`` variables with `4` numeric variables and `8` character variables.
+ Of all variables, the key ones are:
  + `uid` is unique id for each observation;
  + Variables including ``r colnames(homd_df)[3:7]`` contain the basic demographic information about each victim;
  + Variables like ``r colnames(homd_df)[8:11]`` represent the location of the killing;
  + Variable `disposition` includes values like ``r unique(pull(homd_df, disposition))``. A homicide to be considered as `Closed with arrest` when police reported that to be the case, while `Closed without arrest` means there is sufficient evidence but an arrest is impossible. And all other cases were classified as `Open/No arrest`.

**Data mutation**
```{r}
homd_df %>% 
  mutate(
    city_state = str_c(city, ", ", state),
    unsolved = as.numeric(disposition != "Closed by arrest")
  ) %>% 
  filter(city_state != "Tulsa, AL") %>% 
  group_by(city_state) %>% 
  summarize(
    ttl_homicide = n(),
    unsol_homicide = sum(unsolved)
  )
```

