---
title: "p8105_hw5_qw2331"
output: github_document
---

```{r setup, echo = FALSE, message = FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%",
  message = FALSE
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

**Load the data**
```{r}
homd_raw <- read_csv(
  "./data/homicide-data.csv",
  na = c("", "Unknown"))
```

**A brief description**
```{r}
# Using summary or glimpse
summary(homd_raw)
```
+ This dataset contains ``r nrow(homd_raw)`` observations and ``r ncol(homd_raw)`` variables with `4` numeric variables and `8` character variables.
+ Of all variables, the key ones are:
  + `uid` is unique id for each observation;
  + Variables including ``r colnames(homd_raw)[3:7]`` contain the basic demographic information about each victim;
  + Variables like ``r colnames(homd_raw)[8:11]`` represent the location of the killing;
  + Variable `disposition` includes values like ``r unique(pull(homd_raw, disposition))``. A homicide to be considered as `Closed with arrest` when police reported that to be the case, while `Closed without arrest` means there is sufficient evidence but an arrest is impossible. And all other cases were classified as `Open/No arrest`.

**Data mutation**
```{r}
homd_df <- 
  homd_raw %>% 
  mutate(
    city_state = str_c(city, ", ", state),
    status = ifelse(disposition == "Closed by arrest", "solved", "unsolved")
  ) %>% 
  filter(city_state != "Tulsa, AL") %>% 
  relocate(city_state)

homd_df %>% 
  group_by(city_state) %>% 
  summarize(
    ttl_homicide = n(),
    unsol_homicide = sum(status == "unsolved")
  )
```

**Proportion of homicides estimation for Baltimore, MD**
```{r}
# Write a prop_test_function
prop_test_function <- function(city_df) {

  city_summary <- 
  city_df %>% 
  summarize(
    ttl = n(),
    unsol = sum(status == "unsolved")
  )

  city_test <- 
  prop.test(
  pull(city_summary, unsol),
  pull(city_summary, ttl)
)

  return(city_test)
  
}

# Create Baltimore dataframe
baltimore_df <- 
  homd_df %>% 
  filter(city_state == "Baltimore, MD")

prop_test_function(baltimore_df) %>% 
  broom::tidy() %>% 
  select(estimate, conf.low, conf.high)
```

**Run `prop.test` for each city**
```{r}
result_df <- 
  homd_df %>% 
  nest(data = uid:status) %>% 
  mutate(
    test_results = map(data, prop_test_function),
    tidy_results = map(test_results, broom::tidy)
  ) %>% 
  unnest(tidy_results) %>% 
  select(city_state, estimate, starts_with("conf"))

result_df
```

**Make a plot showing estimates and confidence intervals**
```{r, fig.width = 10}
result_df %>% 
  mutate(
    city_state = fct_reorder(city_state, estimate)
  ) %>% 
  ggplot(aes(x = city_state, y = estimate)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) + 
  theme(
    axis.text.x = element_text(angle = 90, vjust = .5, hjust = 1)) + 
  labs(
    x = "City and State",
    y = "Estimation",
    title = "Estimates and CIs for each city"
  )
```


## Problem 2

**Create a dataframe containing data from all participants**
```{r}
file_df <- 
  tibble(
    files = list.files("./data/zip_data/")
  )

longitudial_raw <- 
  file_df %>% 
  mutate(
    file_path = str_c("./data/zip_data/", files),
    data = map(file_path, read_csv)
  )

longitudial_df <- 
  longitudial_raw %>% 
  separate(files, into = c("arm", "subjectID", sep = "_")) %>%
  select(arm, subjectID, data) %>% 
  unnest(data) %>% 
  pivot_longer(
    3:10,
    names_to = "week_num",
    values_to = "data"
  )

```

**Make a spaghetti plot for each group**
```{r, fig.width = 10}
longitudial_df %>% 
  mutate(
    arm = recode(
      arm,
      con = "Control",
      exp = "Experiment"
    )
  ) %>% 
  ggplot(aes(x = week_num, y = data, group = subjectID, color = subjectID)) + 
  geom_line() + 
  facet_grid(. ~ arm) + 
  labs(
    x = "Number of week",
    y = "Results",
    title = "Observations on each subject over time"
  )
```

From the above plots, while the results for the subjects in the experiment group increase over time, the results in the control group keep stable in general.
